Flowchart of Current Algorithm

### 2008-10-30 docs/flowchart/flowchart.tex
added line about what full_rhoh0_evolution does
some minor cleanup

If this is the first step of the calculation ($n=0$), we set
\begin{equation}
S^{\half,\star} = \frac{S^0 + S^1}{2} \enskip ,
\end{equation}
where $S^1$ is found through the iterative process that initializes the calculation.
Otherwise, following the method used in our small-scale low Mach number algorithm
(BDRWZ), we extrapolate to the half-time using the source
terms at the previous and current time levels
\begin{equation}
S^{\nph,\star} = S^n + \frac{\Delta t^n}{2} \frac{S^n - S^{n-1}}{\Delta t^{n-1}} \enskip .
\end{equation}

@@

\item {\bf React Base}$[(\rho h)_0^n,(\overline{\rho \Hnuc})^{(1)},(\overline{\rho\Hext})^n] \rightarrow [(\rho h)_0^{(1)}]$

\item
Define
\begin{eqnarray}
\gammabar^{(1)}        &=& {\rm{\bf Avg}} \left[ \Gamma_1(\rho^{(1)}, p_0^{n}, X_k^{(1)}) \right] \enskip , \\
 {\beta   }_0^{(1)}    &=& \beta   \left(\rho_0^{n}, p_0^{n}, \gammabar^{(1)}\right) \enskip .
\end{eqnarray}
Here $\beta_0$ is computed as described in paper~III, Appendix C.

@@

Next, we need to construct an approximation to the time-centered perturbational pressure,
$\pi,$  and an approximation to the divergence constraint at the end of the
first time step.  As initial approximations, set $S^{1,0} = S^0$,
$\etarho^{-\half} = 0$, $\psi^{-\half} = 0$, and $\pi^{-\half} = 0.$
\begin{enumerate}
  \renewcommand{\theenumi}{{\bf \alph{enumi}}}
  \renewcommand{\labelenumii}{\roman{enumii}.}
  \addtocounter{enumi}{1}

@@

  \begin{enumerate}
  \item Perform steps 1--11 as described above, using 
    $S^{\half,\star} = (S^0 + S^{1,\nu})/2$ in step 1 as described.
    The only other difference in the time advancement is that in step 11
    we define ${\bf V} = (\Ubt^{1,\star} - \Ubt^0)$ and solve
    \begin{equation}  L_\beta^\rho \phi =
      D \left ( \beta_0^{\half} {\bf V} \right) - \beta_0^{\half} \left[ (S^{1}-\overline{S}^{1}) - (S^{0}-\overline{S}^{0}) \right] \enskip . 
    \end{equation}
    (The motivation for this form of the projection in the initial pressure iterations
    is discussed in (cite almgren:bell:crutchfield).)
      We discard the new velocity resulting from this, but keep the new  
      value for $\pi^{\half} = \pi^{-\half} + (1 / \dt) \; \phi.$  
      These steps also yield new scalar data at time $\dt,$ which
      we discard,  and new values for $\etarho^{\half}$ (step 8), $\psi^{\half}$ (step 8), 
      $S^{1,\nu+1}$ (step 10), and $\pi^{\half}$ (step 11), which we keep.
    \item Set $\pi^{-\half} = \pi^{\half}$, $\etarho^{-\half} = \etarho^{\half}$,
      and $\psi^{-\half} = \psi^{\half}$. 
    \end{enumerate}

@@

\begin{enumerate}
\item Why do we only update the temperature at the end of steps 4 and
      8.  This means that at the top of the algorithm, the temperature
      going into {\bf React State} in step 2 does not include the
      effects of the previous reactions.

@@

\item Why for plane parallel, when constructing the full edge state
      (eq.~\ref{eq:rhoXedgestate}) do we simply average to the interface
      instead of doing the 4th order interpolation that is used for the
      full state?

>>>>

If this is the first step of the calculation ($n=0$), we set
\begin{equation}
S^{\myhalf,\star} = \frac{S^0 + S^1}{2} \enskip ,
\end{equation}
where $S^1$ is found through the iterative process that initializes the calculation.
Otherwise, following the method used in our small-scale low Mach number algorithm
(BDRWZ), we extrapolate to the half-time using the source
terms at the previous and current time levels
\begin{equation}
S^{\nph,\star} = S^n + \frac{\Delta t^n}{2} \frac{S^n - S^{n-1}}{\Delta t^{n-1}} \enskip .
\end{equation}

@@

\item {\bf if} ~ {\tt full\_rhoh0\_evolution = T} ~ {\bf then}\\
{\bf React Base}$[(\rho h)_0^n,(\overline{\rho \Hnuc})^{(1)},(\overline{\rho\Hext})^n] \rightarrow [(\rho h)_0^{(1)}]$ \\
{\bf else}\\
$(\rho h)_0^{(1)} = (\overline{\rho h})^{(1)}$\\
{\bf end if}
\item
Define
\begin{eqnarray}
\gammabar^{(1)}        &=& {\rm{\bf Avg}} \left[ \Gamma_1(\rho^{(1)}, p_0^{n}, X_k^{(1)}) \right] \enskip , \\
 {\beta   }_0^{(1)}    &=& \beta   \left(\rho_0^{n}, p_0^{n}, \gammabar^{(1)}\right) \enskip .
\end{eqnarray}
Here $\beta_0$ is computed as described in paper~III, Appendix C.

@@

Next, we need to construct an approximation to the time-centered perturbational pressure,
$\pi,$  and an approximation to the divergence constraint at the end of the
first time step.  As initial approximations, set $S^{1,0} = S^0$,
$\etarho^{-\myhalf} = 0$, $\psi^{-\myhalf} = 0$, and $\pi^{-\myhalf} = 0.$
\begin{enumerate}
  \renewcommand{\theenumi}{{\bf \alph{enumi}}}
  \renewcommand{\labelenumii}{\roman{enumii}.}
  \addtocounter{enumi}{1}

@@

  \begin{enumerate}
  \item Perform steps 1--11 as described above, using 
    $S^{\myhalf,\star} = (S^0 + S^{1,\nu})/2$ in step 1 as described.
    The only other difference in the time advancement is that in step 11
    we define ${\bf V} = (\Ubt^{1,\star} - \Ubt^0)$ and solve
    \begin{equation}  L_\beta^\rho \phi =
      D \left ( \beta_0^{\myhalf} {\bf V} \right) - \beta_0^{\myhalf} \left[ (S^{1}-\overline{S}^{1}) - (S^{0}-\overline{S}^{0}) \right] \enskip . 
    \end{equation}
    (The motivation for this form of the projection in the initial pressure iterations
    is discussed in (cite almgren:bell:crutchfield).)
      We discard the new velocity resulting from this, but keep the new  
      value for $\pi^{\myhalf} = \pi^{-\myhalf} + (1 / \dt) \; \phi.$  
      These steps also yield new scalar data at time $\dt,$ which
      we discard,  and new values for $\etarho^{\myhalf}$ (step 8), $\psi^{\myhalf}$ (step 8), 
      $S^{1,\nu+1}$ (step 10), and $\pi^{\myhalf}$ (step 11), which we keep.
    \item Set $\pi^{-\myhalf} = \pi^{\myhalf}$, $\etarho^{-\myhalf} = \etarho^{\myhalf}$,
      and $\psi^{-\myhalf} = \psi^{\myhalf}$. 
    \end{enumerate}

@@

\begin{enumerate}

\item Why do we only update the temperature at the end of steps 4 and
      8.  This means that at the top of the algorithm, the temperature
      going into {\bf React State} in step 2 does not include the
      effects of the previous reactions.

@@
